# Setup {#sec-setup}

## Software 

## Data

1. **Option 1: Download all the data**. Download and extract **[this zip file <i class="fa fa-file-archive-o" aria-hidden="true"></i>](data/data.zip)** `r paste0("(", round(file.info("data/data.zip")$size/1e6, 2), " Mb)")` with all the data for the entire workshop. This may include additional datasets that we won't use here.
1. **Option 2: Download individual datasets as needed.** 
    - Create a new folder somewhere on your computer that's easy to get to (e.g., your Desktop). Name it `bds`. Inside that folder, make a folder called `data`, all lowercase. 
    - Download individual data files as needed, saving them to the new `bdsr/data` folder you just made. Click to download. If data displays in your browser, right-click and select _Save link as..._ (or similar) to save to the desired location.


```{r}
#| echo: false
#| output: asis
datadir <- "data"
datazip <- file.path(datadir, "data.zip")
datafiles <- 
  list.files(datadir, pattern="\\.csv$|\\.csv\\.gz$") |>
  sort() |>
  grep("\\.html$", x=_, value=TRUE, invert=TRUE) |>
  grep("\\.zip$", x=_, value=TRUE, invert=TRUE) |>
  grep("^_", x=_, value=TRUE, invert=TRUE)
datafiles <- file.path(datadir, datafiles)
cat(paste0("- [", datafiles, "](", datafiles, ")"), sep="\n")
```

```{r}
#| include: false
#| eval: false
if (exists(datazip)) file.remove(datazip)
datafiles <- grep("*.rds|*\\.html|*\\.DS_Store", datafiles, invert=TRUE, value=TRUE)
zip(zipfile=datazip, files = datafiles)
```
